BECKY:\\Bayesian Estimation of Coevolutionary KrYteria

### 2013-07-18 paper/article.tex
Assortment of modifications

% Layout and formatting
\usepackage[margin=1in]{geometry}
\usepackage{csquotes}
\usepackage{fixltx2e}
\usepackage{mathptmx}
\usepackage{setspace}
\usepackage{units}
\frenchspacing

@@

% Math
\usepackage{algorithm2e}

\title{BECKY:\\Bayesian Estimation of Coevolutionary KrYteria}

@@

@@

@@

\begin{figure}
\centering
\begin{subfigure}[b]{0.2\textwidth}
\centering
\begin{pspicture}(1,1)
\psline(0,0.5)(0.5,0.5)
\psline(0.5,0.3)(1,0.3)
\psline(0.5,0.7)(1,0.7)
\psline(0.5,0.3)(0.5,0.7)
\psline[linestyle=dashed](0,0.6)(0.4,0.6)
\psline[linestyle=dashed](0.4,0.4)(1,0.4)
\psline[linestyle=dashed](0.4,0.8)(1,0.8)
\psline[linestyle=dashed](0.4,0.4)(0.4,0.8)
\end{pspicture}
\caption{cospeciation}
\end{subfigure}
\begin{subfigure}[b]{0.2\textwidth}
\centering
\begin{pspicture}(1,1)
\psline(0,0)(1,0)
\psline[linestyle=dashed](0,0.1)(1,0.1)
\psline[linestyle=dashed](0.5,0.1)(0.5,0.3)
\psline[linestyle=dashed](0.5,0.3)(1,0.3)
\end{pspicture}
\caption{duplication}
\end{subfigure}
\begin{subfigure}[b]{0.2\textwidth}
\centering
\begin{pspicture}(1,1)
\psline(0,0)(1,0)
\psline(0,0.4)(1,0.4)
\psline[linestyle=dashed](0,0.1)(1,0.1)
\psline[linestyle=dashed](0.5,0.1)(0.5,0.5)
\psline[linestyle=dashed](0.5,0.5)(1,0.5)\end{pspicture}
\caption{host-shift}
\end{subfigure}
\begin{subfigure}[b]{0.2\textwidth}
\centering
\begin{pspicture}(1,1)
\psline(0,0)(1,0)
\psline[linestyle=dashed](0,0.1)(0.8,0.1)
\rput(0.8,0.1){\textsf{X}}
\end{pspicture}
\caption{loss}
\end{subfigure}
\caption{Diagrams of the four cophylogenetic events considered in my model, which was coined the four-event model by \textcite{Ronquist:2003}, where the host phylogeny and the symbiont dashed. All events are branch events (i.e., they can occur at any point), except cospeciation, which is a nodal event (and thus can occur only when the host speciates).}
\end{figure}

@@

>>>>

% Layout and formatting
\usepackage[margin=1in]{geometry}
\usepackage{acronym}
\usepackage{csquotes}
\usepackage{fixltx2e}
\usepackage{mathptmx}
\usepackage{setspace}
\usepackage{units}
\frenchspacing

@@

% Math
\usepackage{amsmath}
\usepackage{algorithm2e}
\usepackage{mathtools}

\title{BECKY:\\Bayesian Estimation of Coevolutionary KrYteria}
%\author{Arman Bilge}

@@

\begin{acronym}
  \acro{MCMC}{Markov chain Monte Carlo}
  \acro{GTR}{general time reversible}
\end{acronym}

@@

\begin{figure}
\centering
\begin{subfigure}[b]{0.2\textwidth}
\centering
\begin{pspicture}(1,1)
\psline(0,0.5)(0.5,0.5)
\psline(0.5,0.3)(1,0.3)
\psline(0.5,0.7)(1,0.7)
\psline(0.5,0.3)(0.5,0.7)
\psline[linestyle=dashed](0,0.6)(0.4,0.6)
\psline[linestyle=dashed](0.4,0.4)(1,0.4)
\psline[linestyle=dashed](0.4,0.8)(1,0.8)
\psline[linestyle=dashed](0.4,0.4)(0.4,0.8)
\end{pspicture}
\caption{cospeciation}
\end{subfigure}
\begin{subfigure}[b]{0.2\textwidth}
\centering
\begin{pspicture}(1,1)
\psline(0,0)(1,0)
\psline[linestyle=dashed](0,0.1)(1,0.1)
\psline[linestyle=dashed](0.5,0.1)(0.5,0.3)
\psline[linestyle=dashed](0.5,0.3)(1,0.3)
\end{pspicture}
\caption{duplication}
\end{subfigure}
\begin{subfigure}[b]{0.2\textwidth}
\centering
\begin{pspicture}(1,1)
\psline(0,0)(1,0)
\psline(0,0.4)(1,0.4)
\psline[linestyle=dashed](0,0.1)(1,0.1)
\psline[linestyle=dashed](0.5,0.1)(0.5,0.5)
\psline[linestyle=dashed](0.5,0.5)(1,0.5)
\end{pspicture}
\caption{host-shift}
\end{subfigure}
\begin{subfigure}[b]{0.2\textwidth}
\centering
\begin{pspicture}(1,1)
\psline(0,0)(1,0)
\psline[linestyle=dashed](0,0.1)(0.8,0.1)
\rput(0.8,0.1){\textsf{X}}
\end{pspicture}
\caption{loss}
\end{subfigure}
\caption{Diagrams of the four cophylogenetic events considered in my model, which was coined the four-event model by \textcite{Ronquist:2003}, where the host phylogeny and the symbiont dashed. All events are branch events (i.e., they can occur at any point), except cospeciation, which is a nodal event (and thus can occur only when the host speciates).}
\end{figure}

@@

%\begin{equation}
%P\left(M,\Theta_M|D\right) \propto \int\limits_{T_H \times T_S} \overbrace{P\left(d_H|t_H,\theta_H\right)}^{\mathclap{\text{Felsenstein likelihood for host tree}}} \underbrace{P\left(d_S|t_S,\theta_S\right)}_{\mathclap{\text{Felsenstein likelihood for symbiont tree}}} P\left(d_M|M,\theta_M,t_H,t_S\right) P\left(M\right) \textrm{d}T_H \times T_S 
%\end{equation}

\begin{equation}
P\left(m,\Theta|D\right) \propto \int\limits_{T_H \times T_S}  P\left(d_M|m, \theta_M\right) P\left(t_H|d_H,\theta_H\right) P\left(t_S|d_S,\theta_S\right) P\left(\theta_H\right) \textrm{d} t_H t_S 
\end{equation}

This integral can be approximated via a \ac{MCMC} analysis.

Nevertheless, it is possible to model these events on the principle of observation; i.e., what specific event or events are we observing.

For example, we can consider molecular evolution.

@@

The effects of the cophylogenetic likelihood on mixing of the MCMC chain needs to be seriously investigated.
